Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-08-30 parts/intro.tex
more better words

The volunteers were encouraged to create models of objects found in Space~Warps before they were classified as plausible candidates.
Figure~\ref{fig:time} shows the evolution of the total number of models the users generated, models created for systems that turned out to be non candidates were not included.
The first beta version of SpaghettiLens was launched around day 140 and additional features were implemented on the fly.
It saw 8 volunteers with major contributions.
Around day 200 some volunteers started a modelling challenge for the candidate later to be identified as SW~01.
This group of volunteers converged to a set of favorite models that they presented in an online letter after about 65 days and 30 models have been created for this particular system.
At day 820 the first full version of SpaghettiLens was presented online for testing, around the same time the list of identified candidates was available.
At this stage, we can see for example with candidate SW~29, the volunteers converged to a favorable model after 15 models generated in 30 days.

>>>>

The volunteers were encouraged to create models of objects found in Space~Warps before they were classified as plausible candidates.
Figure~\ref{fig:time} shows the evolution of the total number of models the users generated, models created for systems that turned out to be non candidates were not included.
The first beta version of SpaghettiLens was launched around day 140 and additional features were implemented on the fly.
The system was tested by eight major contributors, volunteers that at least generated five models.
Around day 200 a modelling challenge for the candidate later to be identified as SW~01 was proposed.
A group of five volunteers converged to a set of favorite models that they presented in an online letter after about 65 days and 30 models have been created for this particular system.
At day 820 the first full version of SpaghettiLens was presented online for testing, around the same time the list of identified candidates was available.
At this stage, we can see for example with candidate SW~29, the volunteers converged to a favorable model after 15 models generated in 30 days.
